Neuroanatomical priors improve image-based cortical thickness computation: ROI-DiReCT

### 2015-10-19 manuscript.tex
introduction
@@@

Working memory is a temporal process to maintain and manipulate information over short periods of time. WM has been shown to be impaired in many neurological and psychiatric syndromes including Schizophrenia. It was thought to be tightly associated with cognitive deficits in Schizophrenia. WM itself is a complex process which has been multidimensionally related to the psychosis.
Thus, a examination of the underlying neurological mechanism provided us with insight into the causes, progression and even treatment of schizophrenia. There has been abundant imaging studies in this area, but the differences among the tasks and material make it difficult to make a conclusion. There have been evidence of multi-modality deficits: visual spatial, visual object, verbal, and other types of working memory. One popular and original model of WM is a system encoding and maintaining modality-specific short-term memory and central executive component to manipulate the information.

>>>>

Working memory is a temporal process to maintain and manipulate information over short periods of time. WM has been shown to be impaired in many neurological and psychiatric syndromes including Schizophrenia. It was thought to be tightly associated with cognitive deficits in Schizophrenia. WM itself is a complex process which has been multidimensionally related to the psychosis.

Thus, a examination of the underlying neurological mechanism provided us with insight into the causes, progression and even treatment of schizophrenia. There has been abundant imaging studies in this area, but the differences among the tasks and material make it difficult to make a conclusion. There have been evidence of multi-modality deficits: visual spatial, visual object, verbal, and other types of working memory. One popular and original model of WM is a system encoding and maintaining modality-specific short-term memory and central executive component to manipulate the information. Some studies have found evidence for different patterns of functional connectivity during different working memory task conditions (e.g., as a function of load, stimulus type, or task phase).  Such ﬁndings suggest that functional connectivity changes could reﬂect differences in task engagement or responsivity of brain networks to modulation,rather than stable changes that persist across all task states. Some studies have found both impairments in the modality-specific perception component and the later manipulation component. In a recent meta analysis, the author draw attention to a consistent and restricted "core network" emerged form conjunctions across analyses of specific task designs and contrasts. This distributed network was believed to be active in WM task ignoring the task type , stimulus type and WM load and may be act as a base part in WM.
